Papers I Love

### 2019-07-06 texts/dev/PapersILove.tex
.

\subsubsection{Compression}
\begin{enumerate}
\item {Data Compression Using Long Common Strings\\
\url{http://www.cs.brandeis.edu/~dilant/cs175/%5BSiying-Dong%5D.pdf}}
\end{enumerate}

@@

\subsubsection{Data Structures}
\begin{enumerate}
\item {Bitlist New Full-Text Index for Low Space Cost and Efficient Keyword Search\\
\url{http://www.vldb.org/pvldb/vol6/p1522-rao.pdf}}
\end{enumerate}

>>>>

\subsubsection{Compression}
\begin{enumerate}
\item{A Universal Algorithm for Sequential Data Compression\\ \url{	http://citeseer.ist.psu.edu/viewdoc/download?doi=10.1.1.118.8921}}
\item {Data Compression Using Long Common Strings\\
\url{http://www.cs.brandeis.edu/~dilant/cs175/%5BSiying-Dong%5D.pdf}}
\end{enumerate}

@@

\subsubsection{Data Structures}
\begin{enumerate}
	\item{Hashed and Hierarchical Timing Wheels: Data Structures for the Efficient Implementation of a Timer Facility\\ \url{https://web.archive.org/web/20130319034954/https://www.cs.columbia.edu/~nahum/w6998/papers/sosp87-timing-wheels.pdf}}
\item {Bitlist New Full-Text Index for Low Space Cost and Efficient Keyword Search\\
\url{http://www.vldb.org/pvldb/vol6/p1522-rao.pdf}}
\end{enumerate}
